%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% (v1.0, May 16 2024) written by Genki Ogaki (rockstarogk@gmail.com). Compiles with XeLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Shawn}
\familyname{Faberr}
\address{Brooklyn, NY}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{sfaber02@gmail.com} & \mobilephonesymbol\enspace 401-585-9368 & \faGithub\enspace \href{https://www.github.com/sfabore02}{github.com/sfaber03}
\end{tabularx}
\vspace{-2.0mm}

% left column
\begin{minipage}[t]{0.62\textwidth}
\section{EXPERIENCE}
\experienceentry{Peloton Interactive}{Backend Software Engineer}{Dec 2022 - Present}{New York, NY}

\textbf{Key Responsibilities}
\begin{itemize}
    \item 
    \item 
    \item \%.
\end{itemize}
\vspace{1.0mm}

\textbf{Recommendation System for Real Estate Webpages}
\begin{itemize}
    \item Developed machine learning API to provide personalized property recommendations on real estate webpages, enhancing user experience by aligning suggestions with customer preferences.
    \item Chose LightGBM for the recommendation engine due to its compatibility with BigQuery data, achieving 5\% increase in recall@5 compared to existing models.
\end{itemize}
\vspace{1.0mm}

\textbf{Data Validation System}
\begin{itemize}
    \item Participated in developing system to detect data anomalies that could impair machine learning models, including recommendation systems, preventing significant profit loss.
    \item Implemented wrapper interface for AWS Deequ, the core module of system, and developed extensions for various use cases in Scala.
\end{itemize}
\vspace{2.0mm}

\experienceentry{BBB company}{Web Engineer and Math Teacher}{Apr 2019 - Mar 2020}{Kyoto, Japan}

\textbf{Web Page Development and Maintenance}
\begin{itemize}
    \item Deployed websites to promote the founder's initiatives, attracting prospective students and enhancing online visibility.
    \item Built the websites using 3-tier architecture, implemented in Python with Flask framework; containerized with Docker for streamlined maintenance and deployed on GCP to optimize costs.
\end{itemize}
\vspace{2.0mm}

\experienceentry{CCC company}{Quantitative Analyst and Engineer}{Apr 2018 - Mar 2019}{Tokyo, Japan}

\textbf{Price Calculation Module for Binary Options}
\begin{itemize}
    \item Led development of price calculation library, collaborating with IT system department to launch new binary options products (type of financial derivative).
    \item Developed Python library from scratch based on the Black-Scholes model to accurately price binary options.
    \item Replaced outsourced system, enhancing work efficiency and reducing operational time by 3 hours weekly.
\end{itemize}
\vspace{1.0mm}

\textbf{Monitoring of CFDs (Contract for Differences)}
\begin{itemize}
    \item Developed batch processing system to visualize bid prices, trade records, and revenues of CFDs by extracting transaction data from Oracle and creating plots using Python.
\end{itemize}

\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}
\section{SUMMARY}
Skilled data scientist specializing in machine learning and financial engineering with 4 years of experience. Persistent dedication, analytical prowess and strong soft skills for fostering collaborative work relationships.

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Back End & Python, Kotlin, Javascript \\
Front End & HTML, CSS, JavaScript \\
DBMS & PostgreSQL, Redis, DynamoDB \\
OS & macOS, Linux, Windows \\
DevOps & Docker, Git, Jenkins \\
Misc. & AWS, Datadog \\
\end{tabularx}

\section{EDUCATION}
\educationentry{Full-stack web development}{Pursuit}{Queens, NY}
\par
\vspace{3.0mm}
\educationentry{Bachelor of Arts - English}{Burlington College}{Burlington, Vermont}


% \section{SCORES}
% \scoreentry{IELTS (General Training)}{Overall: 7.5}
% \scoreentry{AtCoder}{Rate: 1800+, \, Solved problems: 1800+}
% \scoreentry{LeetCode}{Rate: 2400+, \, Solved problems: 800+}

% \section{LANGUAGES}
% \begin{itemize}
%     \item Japanese (Native)
%     \item English (Advanced)
% \end{itemize}

\section{INTERESTS}
\begin{itemize}
    \item Learning Languages
    \item Fitness
    \item Classical Piano
\end{itemize}
\end{minipage}

\end{document}
